The \dealii Library, Version 9.6

### 2024-08-23 9.6/paper.tex
Add affiliation of Sebastian Kinnewig.

 \author[10,11]{Martin~Kronbichler}
 \affil[10]{Faculty of Mathematics, Ruhr University Bochum,
   Universit\"atsstr.~150, 44780 Bochum, Germany.
 {\texttt{martin.kronbichler@rub.de}}}
 \affil[11]{Institute of Mathematics,
   University of Augsburg,
   Universit\"atsstr.~12a, 86159 Augsburg, Germany.
   }

\author[12]{Matthias~Maier}
\affil[12]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[11,13]{Peter Munch}
 \affil[13]{Uppsala University, Sweden.
  {\texttt{peter.munch@it.uu.se}}}

\author[14]{Magdalena Schreter-Fleischhacker}
 \affil[14]{Institute for Computational Mechanics, Technical University of Munich, Boltzmannstraße 15, 85748 Garching, Germany.
  {\texttt{magdalena.schreter@tum.de}}}

\author[15]{Jan Philipp Thiele}
 \affil[15]{Weierstrass Institute for Applied Analysis and Stochastics,\newline
 Leibniz Institute in Forschungsverbund Berlin e.V.
  {\texttt{thiele@wias-berlin.de}}}

@@

\author[16]{David Wells}
\affil[16]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[17,8]{Vladimir Yushutin}
\affil[17]{Department of Mathematics, University of Tennessee at Knoxville,
	 Knoxville TN 37996-1320, USA.
{\texttt{vyushuti@utk.edu}}}

>>>>

\author[10]{Sebastian~Kinnewig}
\affil[10]{Institute for Applied Mathematics, Scientific Computing, 
           Leibniz University Hannover, 
           Welfengarten 1, 30167 Hannover, Germany
           {\texttt{kinnewig@ifam.uni-hannover.de}}}

 \author[11,12]{Martin~Kronbichler}
 \affil[11]{Faculty of Mathematics, Ruhr University Bochum,
   Universit\"atsstr.~150, 44780 Bochum, Germany.
 {\texttt{martin.kronbichler@rub.de}}}
 \affil[12]{Institute of Mathematics,
   University of Augsburg,
   Universit\"atsstr.~12a, 86159 Augsburg, Germany.
   }

\author[13]{Matthias~Maier}
\affil[13]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[12,14]{Peter Munch}
 \affil[14]{Uppsala University, Sweden.
  {\texttt{peter.munch@it.uu.se}}}

\author[15]{Magdalena Schreter-Fleischhacker}
 \affil[15]{Institute for Computational Mechanics, Technical University of Munich, Boltzmannstraße 15, 85748 Garching, Germany.
  {\texttt{magdalena.schreter@tum.de}}}

\author[16]{Jan Philipp Thiele}
 \affil[16]{Weierstrass Institute for Applied Analysis and Stochastics,\newline
 Leibniz Institute in Forschungsverbund Berlin e.V.
  {\texttt{thiele@wias-berlin.de}}}

@@

\author[17]{David Wells}
\affil[17]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[18,8]{Vladimir Yushutin}
\affil[18]{Department of Mathematics, University of Tennessee at Knoxville,
	 Knoxville TN 37996-1320, USA.
{\texttt{vyushuti@utk.edu}}}
